### 2024-11-29 paper/paper.qmd
Update data section
Describe the dataset and predictors, and plot the graph of each predictors. Then, write the explaination of each graph.

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Yi Tang
thanks: "Code and data are available at: https://github.com/YiTang2/Canadian_Grocery_Analysis.git "
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

Price of each month's coffee of different vendors data is provided by[@citedata]. This dataset records detailed sales about fast-moving consumer goods (FMCG) sold by various vendors, including volia, T&T, Loblaws, SaveOnFoods, Galleria, Metro, NoFrills and Walmart. It is also includes product-level details, such as the product name, current price, historical price (`old_price`), and the corresponding units and price per unit. The data also captures time-specific observations(2024-2-28 to 2024-6-22), with timestamps (nowtime) that can be used to analyze trends over days or months.

In order to simulate data, test simulated data, clean data, test cleaned data, exploratory data analysis and model data, we used R programming language [@citeR] to analyze the data and plot the graphs. Specific libraries that assisted the analysis include `tidyverse` [@citetidyverse], `palmerpenguins` [@palmerpenguins], `knitr` [@citeknitr], `arrow` [@citearrow], `ggplot2` [@citeggplot2],  `dplyr` [@citedplyr],  `here` [@citehere], `kableExtra` [@citekableExtra], `gridExtra`[@citegridExtra], `modelsummary`[@citemodelsummary], `rstanarm`[@citerstanarm].

The inspiration for my data processing came from my desire to study what factors would affect the current price of coffee products from two vendors in different regions of Canada, such as the current price of coffee products from two vendors, Metro and SaveOnFoods. The following variables are the data I selected after cleaning the data:

- `vendor`: The retailer selling the product in Canada.
- `old_price`: The historical price of the product, showing previous pricing or discounts.
- `product_name`: The specific product being sold, providing product-level insights.
- `current_price`: The price of the product at the time of observation.

New variable extracted and transformed from raw data:

- `month`: The month of data collection, extracted from `nowtime`.

Since the variable nowtime only records 4 months, it is considered a lack of Long-Term Trends, which means it's difficult to identify long-term pricing or demand patterns by using short data periods. So I only extracted a new variable—month from date of nowtime, which can simplify temporal analysis and identify trends, such as seasonal monthly pattern with price changes or demand patterns. It allows grouping data for monthly aggregation and supporting seasonality-focused insights or forecasting models.

To provide an preview of the coffee pricing with all potential factors that might affect it. Here, @tbl-sample-analysis-data simply reveals the variation between current price and old price in June for Metro's coffee products.

```{r}
#| label: tbl-sample-analysis-data
#| tbl-cap: "Sample of Analysis Data Showing Products Sold by Both Vendors"
#| echo: false
#| warning: false
#| message: false

# Load the analysis data
analysis_data <- read_parquet(here("data", "02-analysis_data", "analysis_data.parquet"))

# Select the first 10 rows
preview_table <- head(analysis_data, 10)

# Display the table
preview_table |>
  kable(
    col.names = colnames(preview_table),  # Use original column names
    digits = 2,  # Format numeric columns with 2 decimal places
    booktabs = TRUE,  # LaTeX-style formatting
    align = c("l", "l", "r", "r", "c"),  # Align columns (left, right, center)
    format.args = list(big.mark = ",")  # Add thousand separators to numbers
  ) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
```

## Measurement

The dataset from Hammer represents real-world retail activities, capturing product details, vendor listings, and price updates. When vendors update product information, such as pricing or availability, Hammer collects and structures this information into the dataset.

Key fields include vendor, product name, current price, old price, and nowtime. The data is collected through scraping and structured to enable analysis of retail trends, pricing strategies, and market dynamics over time. Each entry serves as a snapshot of a product's presence in the market at a specific time, allowing for focused analyses, like tracking price trends for specific products (e.g., coffee).

## Data Visualization

```{r}
#| label: fig-Hist-of-current-price
#| fig-cap: "Histogram of Current Price"
#| message: false
#| echo: false

# First Graph
ggplot(analysis_data, aes(x = current_price)) +
  geom_histogram(bins = 30, fill = "skyblue", color = "black") +
  labs(x = "Current Price", y = "Frequency") +
  theme_minimal()
```

@fig-Hist-of-current-price shows a notable distribution with significant concentrations around 10 and 20 units. This suggests a pricing tier system where certain types of coffee products might be grouped by price points due to quality, brand, or other market factors. The dual peaks could indicate two main categories of coffee products, possibly differentiated by premium versus regular products.

```{r}
#| label: fig-Hist-of-old-price
#| fig-cap: "Histogram of Old Price"
#| message: false
#| echo: false

# Second Graph

ggplot(analysis_data, aes(x = old_price)) +
  geom_histogram(bins = 30, fill = "salmon", color = "black") +
  labs(x = "Old Price", y = "Frequency") +
  theme_minimal()

```

According to @fig-Hist-of-old-price, the distribution is mainly focused between 5 and 20 units, pointing to a past market strategy where products were clustered around these prices. The consistency in this price range might reflect a stable market before any recent pricing adjustments influenced by external factors like supplier changes or inflation.

```{r}
#| label: fig-Bar-plot-of-old-price
#| fig-cap: "Bar Plot of Old Price"
#| message: false
#| echo: false

# Third Graph

ggplot(analysis_data, aes(x = vendor, fill = vendor)) +
  geom_bar() +
  scale_fill_brewer(palette = "Pastel1") +
  labs(x = "Vendor", y = "Frequency") +
  theme_minimal()
```

In @fig-Bar-plot-of-old-price, the frequency of products available from Metro significantly surpasses that from SaveOnFoods, suggesting that Metro has a larger share of the market or a wider variety of coffee products. This dominance in product offerings could provide Metro with a competitive edge in attracting a broader customer base.

```{r}
#| label: fig-scatter-plot-of-current-vs-old-price
#| fig-cap: "Scatterplot of Current Price vs Old Price"
#| message: false
#| echo: false

# Fourth Graph

ggplot(analysis_data, aes(x = old_price, y = current_price)) +
  geom_point(aes(color = vendor), alpha = 0.6) +
  scale_color_manual(values = c("Metro" = "blue", "SaveOnFoods" = "red")) +
  labs(x = "Old Price", y = "Current Price") +
  theme_minimal()

```

The positive relationship shown in @fig-scatter-plot-of-current-vs-old-price here indicates that current prices are influenced by their historical prices, maintaining a proportional increase or decrease. This trend suggests a pricing policy that adjusts prices based on previous benchmarks while taking into account factors like cost adjustments or market demand.

```{r}
#| label: fig-barplot-of-old-price
#| fig-cap: "Boxplot of Current Price by Vendor"
#| message: false
#| echo: false

# Fifth Graph
ggplot(analysis_data, aes(x = vendor, y = current_price)) +
  geom_boxplot() +
  geom_jitter(alpha = 0.3, width = 0.15, height = 0) +
  labs(
    x = "Vendor",
    y = "Current Price"
  ) +
  theme_minimal()

```

@fig-Bar-plot-of-old-price highlights how each vendor prices their products within the market. It shows that both vendors offer a wide range of prices, yet the spread and density of the data points may indicate Metro’s pricing strategy targets both lower and upper market segments, whereas SaveOnFoods might be focusing on a specific niche.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-29 paper/paper.qmd
Update Paper
Update the model and results part of the paper. And put all related graph to the appendix.

@@
 library(palmerpenguins)
+library(knitr)
+library(arrow)
+library(ggplot2)
+library(dplyr)
+library(here)
+library(kableExtra)
+library(gridExtra)
+library(modelsummary)
+library(rstanarm)
 ```
@@
 
-# Model
+# Model {#sec-model}
 
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+The goal of our Bayesian multiple linear regression is to investigate the factors that influence the current price of coffee in our dataset.
+Specifically, we try7  to understand how historical pricing, vendor differences, and seasonal monthly pattern affect current coffee prices.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y_i$ as the current price of coffee for the $i$-th observation in the dataset. The predictors include:
+
+- $x_{1i}$, the old price of the coffee,
+- $x_{2i}$, dummy variable for the vendor, where:\
+$x_{2i}$ = 1: Vendor is "SaveOnFoods"; 
+$x_{2i}$ = 0: Vendor is "Metro",
+- $x_{3i}$, the numeric month variable.
+
+The model is formulated as follows:
 
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma), \\
+\mu_i &= \alpha + \beta_1 \cdot x_{1i} + \beta_2 \cdot x_{2i} + \beta_3 \cdot x_{3i}, \\
+\alpha &\sim \mbox{Normal}(0, 2.5), \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5), \\ 
+\beta_2 &\sim \mbox{Normal}(0, 2.5), \\
+\beta_3 &\sim \mbox{Normal}(0, 2.5), \\
+\sigma &\sim \mbox{Exponential}(1).
 \end{align}
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+This model describes the relationship between the current price of coffee $\left(y_i\right)$ and three predictors: the old price of coffee $\left(x_{1 i}\right)$, a categorical vendor variable $\left(x_{2 i}\right)$ indicating whether the vendor is "Metro" or "SaveOnFoods," and a numeric variable for the month $\left(x_{3 i}\right)$.
+The response variable $\left(y_i\right)$ is modeled as normally distributed with mean $\mu_i$ and standard deviation $\sigma$.
+The mean $\mu_i$ is defined as a linear combination of these predictors, with coefficients $\beta_1, \beta_2$, and $\beta_3$, and an intercept $\alpha$.
+Prior distributions for the parameters are specified, including normal priors for $\alpha$ and the coefficients, and an exponential prior for $\sigma$.
+Intercept $\alpha$ represents the baseline mean current price for Metro if $x_{2i}$ = 1; otherwise when $x_{2i}$ = 0, it represents the mean current price for SaveOnFoods.
+Also, when old price and month is equal to 0, the intercept is not meaningful.
+Coefficient $\beta_1$ captures how changes in the old price affect the current price.
+Coefficient $\beta_2$ measures the difference in the mean coffee price between SaveOnFoods ($x_{2i}$ = 1) and Metro ($x_{2i}$ = 0).
+Coefficient $\beta_3$ reflects how the month influences current pricing, potentially capturing seasonal effects.
+
+To implement this Bayesian model, we use the `rstanarm` package [@citerstanarm] in `R` [@citeR].
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+The Bayesian Multiple Linear Regression (MLR) model is a suitable choice for analyzing the relationship between `current_price` (the dependent variable) and the predictors in the dataset.
+The dependent variable is continuous, and the Bayesian framework assumes a normal distribution for the response, which aligns well with the nature of coffee prices.
+This model captures the linear relationships between `old_price` (continuous), `vendor` (categorical, represented as a dummy variable), and `month` (numeric).
+These predictors are assumed to have additive effects on the response, which fits the linear regression framework.
+Logistic regression is used when the outcome variable is binary (e.g.
+0 or 1).
+However, in our dataset, the dependent variable, `current_price`, is continuous.
+Since logistic regression cannot model continuous outcomes, it is unsuitable for this analysis.
+Also, poisson or negative binomial regression is typically applied when the response variable represents count data (e.g., the number of events occurring in a fixed period).
+`current_price` does not represent counts but rather continuous pricing data.
+Thus, these models do not align with the nature of the dependent variable.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+## Model validation
 
-# Results
+@fig-ppcheck-and-posterior-vs-prior shows that our model accurately captures the central tendency of the data, though there are some deviations in the tail ends suggesting that the fit could be improved for extreme values.
+Additionally, the parameter estimation comparison chart highlights that most parameter estimates closely align with their priors, indicating a strong influence of prior settings on the estimates, especially under limited data.
+This is particularly evident with the vendorSaveOnFoods parameter, where its posterior distribution significantly diverges from others, hinting at potential anomalies in data sources or unique behaviors that warrant further investigation.
 
-Our results are summarized in @tbl-modelresults.
+@fig-trace-plot illustrate that our Bayesian model parameters are converging and demonstrating stability, essential for robust statistical inference.
+The slight oscillation of the intercept around -0.5 indicates minor variability.
+Meanwhile, the old price coefficient shows remarkable consistency at approximately 0.77, underlining dependable estimates.
+The month parameter's minor fluctuations suggest a subtle yet consistent temporal effect.
+The vendorSaveOnFoods coefficient consistently remains near -0.6, indicating a persistently negative price influence compared to Metro.
+Finally, sigma's stability around 1.75 ensures the model's error variability is well-accounted for.
+These observations collectively affirm that the model's parameters are effectively calibrated, offering a reliable foundation for understanding the influences on coffee prices.
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
+In @fig-rhat-plot analysis of coffee product pricing in Canada, the use of the $\hat{R}$ values to assess model convergence reveals that all parameters have $\hat{R}$ values below 1.05, indicating excellent convergence of the model.
+This result validates the reliability of our model in estimating coffee prices and ensures the robustness of the analysis outcomes.
+It allows us to trust the model outputs, providing a solid foundation for further strategic decision-making and market analysis.
 
-library(rstanarm)
+# Results {#sec-results}
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
+@tbl-model-summary indicates a robust fit with a high $R^2$ of 0.900, suggesting a strong explanatory power of the model regarding the variance in coffee product prices.
+The model's parameters show that the old price of coffee (coefficient = 0.77) has a significant positive influence on the current price, suggesting that past pricing trends are good predictors of current pricing strategies.
+Vendor impact, specifically SaveOnFoods, shows a negative association with current price (coefficient = -0.61), indicating that coffee products from SaveOnFoods tend to be cheaper compared to Metro.
+Additionally, the month coefficient (0.06) implies a slight monthly variation in coffee pricing.
+The model's predictive performance is validated by low WAIC and LOOIC scores, and a small RMSE of 1.75, enhancing confidence in the reliability of its predictions.
 
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
+@fig-credibility-interval llustrates the posterior distributions for the parameters in your Bayesian regression model, analyzing factors influencing coffee prices.
+The intercept shows a slight positive baseline effect.
+The old price of coffee strongly and positively affects the current price, indicating a direct relationship.
+The month variable shows a minimal and variable impact.
+SaveOnFoods, as a vendor, is associated with lower prices compared to Metro.
+The sigma parameter, indicating the model's error variance, shows a sharp and precise estimation, suggesting consistent variability in the data explained by the model.
 
@@
 
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
+# Model details
 ```{r}
@@
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
+#| label: fig-ppcheck-and-posterior-vs-prior
 #| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
+#| fig-cap: "PPcheck & Posterior vs Prior"
 #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
 
-pp_check(first_model) +
+Coffee_product_pricing <-
+  readRDS(file = here::here("models/Coffee_product_pricing.rds"))
+
+pp_check(Coffee_product_pricing) +
   theme_classic() +
@@
 
-posterior_vs_prior(first_model) +
+posterior_vs_prior(Coffee_product_pricing) +
   theme_minimal() +
@@
 
-## Diagnostics
+```{r}
+#| label: tbl-model-summary
+#| tbl-cap: "Model summary of Coffee product pricing"
+#| eval: true
+#| echo: false
+#| warning: false
+#| message: false
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+# Generate model summary table
+modelsummary(
+  list(
+    "Coffee product pricing" = Coffee_product_pricing
+  ),
+  fmt = 2
+)
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+```
 
 ```{r}
+#| label: fig-credibility-interval
+#| fig-cap: "credibility interval"
+#| eval: true
 #| echo: false
+#| warning: false
+#| message: false
+
+plot(
+  Coffee_product_pricing,
+  "areas"
+)
+```
+
+```{r}
+#| label: fig-trace-plot
+#| fig-cap: "Trace plot"
 #| eval: true
+#| echo: false
+#| warning: false
 #| message: false
+
+plot(Coffee_product_pricing, "trace")
+
+```
+
+```{r}
+#| label: fig-rhat-plot
+#| fig-cap: "R-hat plot"
+#| eval: true
+#| echo: false
 #| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
+#| message: false
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
+plot(Coffee_product_pricing, "rhat")
 ```

### 2024-11-29 paper/paper.qmd
Update Introduction and discussion part
Fill up Introduction and Discussion with several aspects. Improve the reference. Give title and subtitle. Then write Abstract. Finally, render it

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Assessing the Multifaceted Influences on Current Coffee Prices"
+subtitle: "Coffee Pricing in Canadian Grocery Stores: Current Prices Strongly Shaped by Historical Trends"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper investigates the factors influencing coffee product prices in Canadian grocery stores, focusing on historical prices, vendor differences, and seasonal trends.
+Using a Bayesian multiple linear regression model, the study reveals that historical prices have the most significant positive impact on current prices, while vendor differences and seasonal variations also play measurable roles.
+These findings highlight how past prices serve as a benchmark for current pricing strategies, emphasizing the importance of historical data in retail decision-making.
+The results contribute to understanding the dynamics of coffee pricing and provide insights for optimizing retail pricing strategies and future research directions."
 format: pdf
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 
-Overview paragraph
+Consuming goods is probably the most common thing in everyone's life.
+Consumers are also most concerned about the price of goods and whether there is a price premium.
+What is the basis for pricing, the purchasing power of consumers?
+Or the cost of each intermediate goods, etc.
+This paper combines the product data of Canadian grocery stores with the raw data, and uses the current price as the outcome predictor to find the factors that may affect it.
+And I selected the most intuitive potential influencing factor - old price - for analysis.
+I also selected two vendors located in eastern and western Canada: Metro and SaveOnFoods, and different months to analyze possible seasonal trends.
 
-Estimand paragraph
+In the analysis of coffee products pricing in Canadian grocery stores, the estimand is the effect of variables like historical prices (`old_price`), month of the year (`month`), and specific vendors (`vendor`), such as Metro and SaveOnFoods, on the current prices of coffee products.
+This paper estimates this effect using a Bayesian MLR model applied to collected dataset, which is to quantify how these factors influence the pricing of coffee in the market.
 
-Results paragraph
+The finding of this paper is that the old price of coffee has a more significant positive impact on the current price among so many predictors.
+Based on this, my guess is that suppliers rely on past price data as a benchmark for setting new prices, which may to maintain the consistency in price levels expected by customers.
+Also due to the lack of data on coffee products in certain months, the analysis of seasonal monthly pattern effect cannot be established.
+This is very critical and important because it can reflect from a basic level the topic that this paper is most concerned about, which is what will affect the current price.
 
-Why it matters paragraph
+The paper is structured as following: @sec-data describes the data used for analysis, @sec-model describes how to set up, justify and validate the model, @sec-result tells the finding of the data and model, @sec-discussion discusses the implication, potential problems, and future expectations.
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+\newpage
 
@@
 
-### Model justification
+## Model justification
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+## Overall findings and Implication {#sec-first-point}
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+This research conducted a detailed examination of coffee product pricing across major Canadian grocery store chains, specifically Metro and SaveOnFoods.
+By utilizing a regression model, the study uncover how historical price data (by month) can predict current coffee prices.
+This approach not only helped identify pricing trends but also provided a systematic framework to analyze the economic factors influencing those trends.
 
-## Second discussion point
+The findings highlight a dynamic interaction between past and present pricing strategies, underscoring the influence of historical prices on current market behaviors.
+This analysis reveals that historical prices are strong predictors of current prices, suggesting that vendors likely use past data as a benchmark for future pricing decisions.
+This could imply a strategy focused on maintaining market stability and optimizing profit margins, which is crucial in a competitive retail environment.
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+## Additional Insights from the Data Analysis
 
-## Third discussion point
+The coffee products prices are influenced by more than just historical trends; they also respond to a range of external economic factors.
+The study highlights how variations in coffee prices align with broader economic indicators like inflation rates and consumer demand.
+This insight is crucial for understanding the dynamic nature of the coffee market, suggesting that vendors adjust their pricing strategies not only based on past price behavior but also in reaction to economic conditions.
+This deeper understanding of price adjustments helps illustrate the broader economic landscape within which these businesses operate, emphasizing the strategic decisions vendors make in response to economic pressures.
+This analysis significantly enriches our understanding of market behaviors and the economic strategies that drive vendor actions in the competitive grocery sector.
 
-## Weaknesses and next steps
+## Shortcomes and Future outlook
 
-Weaknesses and next steps should also be included.
+### Limitation
+This study integrates two distinct raw datasets to construct the analysis dataset, which presents unique challenges due to varying variable names and formats.
+The process involved carefully aligning these variables to ensure consistency and accuracy in the dataset used for modeling.
+This integration underscores the importance of meticulous data preparation in ensuring the reliability of the results obtained from statistical analyses.
+
+A significant limitation of this study is the absence of geographic data for the vendors.
+Although our analysis provides insights into the pricing strategies of Metro and SaveOnFoods, we lack the data to explore how geographical location influences pricing strategies across Canada.
+Metro and SaveOnFoods operate in different regions of Canada, potentially the Eastern and Western parts, and it is plausible that regional economic conditions, competition, and consumer demographics could affect pricing strategies.
+The absence of this data restricts our ability to analyze and understand regional pricing dynamics comprehensively.
+lack of month: only have data of coffee prouduct pricing in June to November.
+
+### Weaknesses and next steps
+While the model provides valuable insights, there are limitations due to the dataset only covering a short period (June to November).
+This limits the ability to analyze long-term trends or seasonal impacts beyond this timeframe.
+Additionally, the model assumes linear relationships among variables, which may not fully capture more complex dynamics in price fluctuations.
+
+Future research could expand the timeframe of data collection to include multiple years to better understand long-term trends and seasonal variations.
+Incorporating additional variables such as promotional activities, competitor prices, and economic indicators could also enrich the analysis.
+Further, exploring non-linear models or machine learning approaches may provide deeper insights into the pricing strategies of different vendors.
+To address these limitations, future research should focus on acquiring and integrating geographic data into the analysis.
+This would allow for a more detailed examination of how location-specific factors influence pricing, enhancing our understanding of regional market behaviors.
+Exploring geographical influences on pricing can reveal targeted strategies that vendors might use to cater to local consumer preferences or to respond to regional competition.
+Incorporating such data would significantly enrich the analytical framework and potentially yield insights that could inform more localized or region-specific business strategies for these vendors.
 

### 2024-11-29 paper/paper.qmd
Update Readme
Update ReadME and delete file that is not be used.

@@
 #| label: fig-Hist-of-current-price
-#| fig-cap: "Histogram of Current Price"
+#| fig-cap: "Frequency of Current Price"
 #| message: false
@@
 #| label: fig-Hist-of-old-price
-#| fig-cap: "Histogram of Old Price"
+#| fig-cap: "Frequency of Old Price"
 #| message: false
@@
 ```{r}
-#| label: fig-Bar-plot-of-old-price
-#| fig-cap: "Bar Plot of Old Price"
+#| label: fig-Bar-plot-of-vendor
+#| fig-cap: "Frequency of Vendor"
 #| message: false
@@
 #| label: fig-scatter-plot-of-current-vs-old-price
-#| fig-cap: "Scatterplot of Current Price vs Old Price"
+#| fig-cap: "Current Price vs Old Price"
 #| message: false
@@
 #| label: fig-barplot-of-old-price
-#| fig-cap: "Boxplot of Current Price by Vendor"
+#| fig-cap: "Current Price by Vendor"
 #| message: false
@@
 
-@tbl-model-summary indicates a robust fit with a high $R^2$ of 0.900, suggesting a strong explanatory power of the model regarding the variance in coffee product prices.
+@tbl-model-summary indicates a strong fit with a high $R^2$ of 0.900, suggesting a strong explanatory power of the model regarding the variance in coffee product prices.
 The model's parameters show that the old price of coffee (coefficient = 0.77) has a significant positive influence on the current price, suggesting that past pricing trends are good predictors of current pricing strategies.
@@
 #| label: fig-credibility-interval
-#| fig-cap: "credibility interval"
+#| fig-cap: "Credibility Interval of Coffee products pricing"
 #| eval: true
@@
 #| label: fig-trace-plot
-#| fig-cap: "Trace plot"
+#| fig-cap: "Trace plot of Coffee products pricing"
 #| eval: true
@@
 plot(Coffee_product_pricing, "trace")
+```
+
+```{r}
+
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-trace-plot
+#| fig-cap: "Trace plot of Party"
+#| fig-subcap: ["Trace plot of Intercept", "Trace plot of old_price", "Trace plot of month", "Trace plot of vendor: SaveOnFoods"]
+#| layout-ncol: 3
+
+plot(Coffee_product_pricing, "trace", "(Intercept)")
+plot(Coffee_product_pricing, "trace", "old_price")
+plot(Coffee_product_pricing, "trace", "month")
+plot(Coffee_product_pricing, "trace", "vendorSaveOnFoods")
 
@@
 #| label: fig-rhat-plot
-#| fig-cap: "R-hat plot"
+#| fig-cap: "R-hat plot of Coffee products pricing"
 #| eval: true

### 2024-11-29 scripts/05-model_data.R

@@ -9,9 +9,6 @@
 
 
 
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-02 paper/paper.qmd
Update paper and script
Filling context into my paper and try to use styler to make my script nice.

@@
 library(rstanarm)
+library(styler)
 ```
+
+\newpage
 
@@
 
-Consuming goods is probably the most common thing in everyone's life.
-Consumers are also most concerned about the price of goods and whether there is a price premium.
-What is the basis for pricing, the purchasing power of consumers?
-Or the cost of each intermediate goods, etc.
-This paper combines the product data of Canadian grocery stores with the raw data, and uses the current price as the outcome predictor to find the factors that may affect it.
-And I selected the most intuitive potential influencing factor - old price - for analysis.
-I also selected two vendors located in eastern and western Canada: Metro and SaveOnFoods, and different months to analyze possible seasonal trends.
+Consuming goods is an integral part of everyone’s daily life, with pricing being a major factor that influences consumer behavior.[@arnot2006ethical] People are particularly interested in the price of goods, and whether there is a price premium or discount.
+What determines these prices?
+Is it the purchasing power of consumers, or perhaps the cost associated with each stage of production?
+This paper seeks to answer some of these questions by combining product data from Canadian grocery stores with additional raw data to identify key factors that influence product pricing.
+Specifically, we focus on coffee products and use the current price as the outcome variable, aiming to understand the influences behind it.
 
-In the analysis of coffee products pricing in Canadian grocery stores, the estimand is the effect of variables like historical prices (`old_price`), month of the year (`month`), and specific vendors (`vendor`), such as Metro and SaveOnFoods, on the current prices of coffee products.
-This paper estimates this effect using a Bayesian MLR model applied to collected dataset, which is to quantify how these factors influence the pricing of coffee in the market.
+To explore this, I chose one of the most intuitive factors: the old price, since historical pricing often influences how vendors set current prices.
+Additionally, I included data from two vendors—Metro and SaveOnFoods—located in different parts of Canada to investigate any differences in pricing strategies between the eastern and western regions.
+The inclusion of month allows us to explore potential seasonal trends in coffee pricing, assessing whether specific times of the year see significant price variations.
 
-The finding of this paper is that the old price of coffee has a more significant positive impact on the current price among so many predictors.
-Based on this, my guess is that suppliers rely on past price data as a benchmark for setting new prices, which may to maintain the consistency in price levels expected by customers.
-Also due to the lack of data on coffee products in certain months, the analysis of seasonal monthly pattern effect cannot be established.
-This is very critical and important because it can reflect from a basic level the topic that this paper is most concerned about, which is what will affect the current price.
+In this study of coffee pricing strategies in Canadian grocery stores, the focus is on estimating how historical prices (old price), time of year (month), and vendor characteristics (vendor) affect current coffee prices.
+Using a Bayesian multiple linear regression model, I estimated these effects to better understand the pricing dynamics of coffee products and to determine how much each factor contributes to pricing decisions in the market.
+
+The findings reveal that the old price has the most significant positive impact on current coffee prices among all the predictors considered.
+This suggests that vendors heavily rely on historical prices when determining current prices, possibly to maintain a level of consistency that consumers expect.
+Due to a lack of data for some months, it was challenging to establish a definitive analysis of seasonal trends, though this aspect remains an important factor for understanding pricing behavior comprehensively.
 
 The paper is structured as following: @sec-data describes the data used for analysis, @sec-model describes how to set up, justify and validate the model, @sec-result tells the finding of the data and model, @sec-discussion discusses the implication, potential problems, and future expectations.
-
-\newpage
 
@@
 This dataset records detailed sales about fast-moving consumer goods (FMCG) sold by various vendors, including volia, T&T, Loblaws, SaveOnFoods, Galleria, Metro, NoFrills and Walmart.
-It is also includes product-level details, such as the product name, current price, historical price (`old_price`), and the corresponding units and price per unit.
+It is also includes product-level details, such as the product name, current price, historical price (old price), and the corresponding units and price per unit.
 The data also captures time-specific observations(2024-2-28 to 2024-6-22), with timestamps (nowtime) that can be used to analyze trends over days or months.
@@
 In order to simulate data, test simulated data, clean data, test cleaned data, exploratory data analysis and model data, we used R programming language [@citeR] to analyze the data and plot the graphs.
-Specific libraries that assisted the analysis include `tidyverse` [@citetidyverse], `palmerpenguins` [@palmerpenguins], `knitr` [@citeknitr], `arrow` [@citearrow], `ggplot2` [@citeggplot2],  `dplyr` [@citedplyr],  `here` [@citehere], `kableExtra` [@citekableExtra], `gridExtra`[@citegridExtra], `modelsummary`[@citemodelsummary], `rstanarm`[@citerstanarm].
+The folder structure for this paper follows the startup folder created by [@rohan].
+It is very helpful in keeping everything organized.
+I also referenced many of the examples and techniques provided by Telling Stories with Data [@alexander2023telling], which helped me understand how to visualize the data and communicate the findings effectively.
+Specific libraries that assisted the analysis include `tidyverse` [@citetidyverse], `knitr` [@citeknitr], `arrow` [@citearrow], `ggplot2` [@citeggplot2],  `dplyr` [@citedplyr],  `here` [@citehere], `kableExtra` [@citekableExtra], `gridExtra`[@citegridExtra], `modelsummary`[@citemodelsummary], `rstanarm`[@citerstanarm].
 
 The inspiration for my data processing came from my desire to study what factors would affect the current price of coffee products from two vendors in different regions of Canada, such as the current price of coffee products from two vendors, Metro and SaveOnFoods.
-The following variables are the data I selected after cleaning the data:
-
-- `vendor`: The retailer selling the product in Canada.
-- `old_price`: The historical price of the product, showing previous pricing or discounts.
-- `product_name`: The specific product being sold, providing product-level insights.
-- `current_price`: The price of the product at the time of observation.
-
-New variable extracted and transformed from raw data:
-
-- `month`: The month of data collection, extracted from `nowtime`.
+@tbl-variable are the data I selected after cleaning the data, and new variable `month` extracted and transformed from raw data also.
 
@@
 It allows grouping data for monthly aggregation and supporting seasonality-focused insights or forecasting models.
+
+```{r}
+#| label: tbl-variable
+#| tbl-cap: "Variables and their Definitions for the Coffee Product Pricing."
+#| echo: false
+#| message: false
+#| warning: false
+#| tbl-pos: H
+
+# Define the table with adjusted column widths and formatting
+variable_table <- data.frame(
+  Variable = c("vendor", "old price", "current price", "product name", "month"),
+  Definition = c(
+    "The retailer selling the product in Canada.",
+    "The historical price of the product, showing previous pricing or discounts.",
+    "The price of the product at the time of observation..",
+    "The specific product being sold, providing product-level insights",
+    "The month of data collection, extracted from 'nowtime'"
+  )
+)
+
+kable(variable_table, col.names = c("Variable", "Definition"),
+      format = "latex", booktabs = TRUE, linesep = "") %>%
+  column_spec(1, bold = TRUE, width = "15em") %>%
+  column_spec(2, width = "20em")  # Adjust the width to allow for more text in the definition column
+```
 
@@
 
-The dataset from Hammer represents real-world retail activities, capturing product details, vendor listings, and price updates.
-When vendors update product information, such as pricing or availability, Hammer collects and structures this information into the dataset.
+The dataset from Hammer provides a comprehensive representation of real-world retail activities, capturing key elements such as product details, vendor listings, and price updates.
+When vendors make updates to product information, including pricing changes or availability adjustments, Hammer gathers and organizes this data into a structured dataset.
+This ensures that the dataset remains accurate and reflective of current retail conditions.
 
-Key fields include vendor, product name, current price, old price, and nowtime.
-The data is collected through scraping and structured to enable analysis of retail trends, pricing strategies, and market dynamics over time.
-Each entry serves as a snapshot of a product's presence in the market at a specific time, allowing for focused analyses, like tracking price trends for specific products (e.g., coffee).
+The dataset includes essential fields such as vendor, product name, current price, old price, and a timestamp referred to as nowtime.
+The data is collected through scraping and is systematically structured to support an in-depth analysis of retail trends, pricing strategies, and overall market dynamics across different periods.
+Each record captures a snapshot of a product’s market presence at a given time, enabling targeted analyses like monitoring price fluctuations for specific products, such as coffee.
+By offering such detailed and time-specific information, the dataset provides a valuable foundation for understanding the evolving dynamics of retail pricing and vendor strategies.
 
@@
 
+## Outcome variables
+
+The outcome variable for this analysis is the current price of coffee products.
+This variable is crucial for understanding the dynamics of pricing in the retail market, as it reflects the final cost faced by consumers.
+Analyzing the current price helps uncover patterns in how vendors adjust prices over time, respond to market conditions, and compete in a fluctuating retail environment.
+By focusing on the current price, we can measure the impact of historical trends, vendor-specific strategies, and seasonal changes on pricing decisions.
+
+## Predictor variables
+
+The predictor variables selected from the raw dataset are old price, month, and vendor.
+The old price serves as a predictor because it provides valuable insight into how past pricing decisions influence current prices.
+Vendors often make incremental adjustments based on historical pricing data, consumer behavior, and market reactions, which makes it a key factor in understanding pricing strategies.
+Month is included to account for possible seasonal trends in pricing, as consumer demand and promotional activities often vary throughout the year, potentially impacting coffee prices.
+Lastly, vendor is used to examine pricing variations between Metro and SaveOnFoods.
+Each vendor may have distinct pricing approaches based on factors like target market, cost structures, or regional positioning, and including this variable enables a comparative analysis of vendor-specific pricing dynamics.
+
 # Model {#sec-model}
@@
 The goal of our Bayesian multiple linear regression is to investigate the factors that influence the current price of coffee in our dataset.
-Specifically, we try7  to understand how historical pricing, vendor differences, and seasonal monthly pattern affect current coffee prices.
+Specifically, we try  to understand how historical pricing, vendor differences, and seasonal monthly pattern affect current coffee prices.
 
@@
 
-- $x_{1i}$, the old price of the coffee,
-- $x_{2i}$, dummy variable for the vendor, where:\
-$x_{2i}$ = 1: Vendor is "SaveOnFoods"; 
-$x_{2i}$ = 0: Vendor is "Metro",
-- $x_{3i}$, the numeric month variable.
+- $X_{\text{Old Price},i}$, the old price of the coffee,
+- $X_{\text{Vendor},i}$, dummy variable for the vendor, where:\
+$X_{\text{Vendor},i}$ = 1: Vendor is "SaveOnFoods"; 
+$X_{\text{Vendor},i}$ = 0: Vendor is "Metro",
+- $X_{\text{Month},i}$, the numeric month variable.
 
@@
 y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma), \\
-\mu_i &= \alpha + \beta_1 \cdot x_{1i} + \beta_2 \cdot x_{2i} + \beta_3 \cdot x_{3i}, \\
+\mu_i &= \alpha + \beta_1 \cdot X_{\text{Old Price},i} + \beta_2 \cdot X_{\text{Vendor},i} + \beta_3 \cdot X_{\text{Month},i}, \\
 \alpha &\sim \mbox{Normal}(0, 2.5), \\
@@
 
-This model describes the relationship between the current price of coffee $\left(y_i\right)$ and three predictors: the old price of coffee $\left(x_{1 i}\right)$, a categorical vendor variable $\left(x_{2 i}\right)$ indicating whether the vendor is "Metro" or "SaveOnFoods," and a numeric variable for the month $\left(x_{3 i}\right)$.
-The response variable $\left(y_i\right)$ is modeled as normally distributed with mean $\mu_i$ and standard deviation $\sigma$.
+This model describes the relationship between the current price of coffee $y_i$ and three predictors: the old price of coffee $X_{\text{Old Price},i}$, a categorical vendor variable $X_{\text{Vendor},i}$ indicating whether the vendor is "Metro" or "SaveOnFoods," and a numeric variable for the month $X_{\text{Month},i}$.
+The response variable $y_i$ is modeled as normally distributed with mean $\mu_i$ and standard deviation $\sigma$.
 The mean $\mu_i$ is defined as a linear combination of these predictors, with coefficients $\beta_1, \beta_2$, and $\beta_3$, and an intercept $\alpha$.
 Prior distributions for the parameters are specified, including normal priors for $\alpha$ and the coefficients, and an exponential prior for $\sigma$.
-Intercept $\alpha$ represents the baseline mean current price for Metro if $x_{2i}$ = 1; otherwise when $x_{2i}$ = 0, it represents the mean current price for SaveOnFoods.
+Intercept $\alpha$ represents the baseline mean current price for Metro if $X_{\text{Vendor},i}$ = 1; otherwise when $X_{\text{Vendor},i}$ = 0, it represents the mean current price for SaveOnFoods.
 Also, when old price and month is equal to 0, the intercept is not meaningful.
 Coefficient $\beta_1$ captures how changes in the old price affect the current price.
-Coefficient $\beta_2$ measures the difference in the mean coffee price between SaveOnFoods ($x_{2i}$ = 1) and Metro ($x_{2i}$ = 0).
+Coefficient $\beta_2$ measures the difference in the mean coffee price between SaveOnFoods ($X_{\text{Vendor},i}$ = 1) and Metro ($X_{\text{Vendor},i}$ = 0).
 Coefficient $\beta_3$ reflects how the month influences current pricing, potentially capturing seasonal effects.
@@
 
-The Bayesian Multiple Linear Regression (MLR) model is a suitable choice for analyzing the relationship between `current_price` (the dependent variable) and the predictors in the dataset.
+The Bayesian Multiple Linear Regression (MLR) model is a suitable choice for analyzing the relationship between `current price` (the dependent variable) and the predictors in the dataset.
 The dependent variable is continuous, and the Bayesian framework assumes a normal distribution for the response, which aligns well with the nature of coffee prices.
-This model captures the linear relationships between `old_price` (continuous), `vendor` (categorical, represented as a dummy variable), and `month` (numeric).
+This model captures the linear relationships between `old price` (continuous), `vendor` (categorical, represented as a dummy variable), and `month` (numeric).
 These predictors are assumed to have additive effects on the response, which fits the linear regression framework.
@@
 0 or 1).
-However, in our dataset, the dependent variable, `current_price`, is continuous.
+However, in our dataset, the dependent variable, `current price`, is continuous.
 Since logistic regression cannot model continuous outcomes, it is unsuitable for this analysis.
@@
 
-## Additional Insights from the Data Analysis
+## Additional understanding from the Data Analysis
 
@@
 # Appendix {-}
+
+# Idealized Survey and Methodology
+
+To address the collection of data regarding coffee prices through an idealized survey and methodology, we have meticulously designed a survey that aligns with best practices in research and data collection[@citedata].
+The survey begins with an introductory section, welcoming participants to the "Coffee Price Insights Survey." This introduction serves to inform respondents of the purpose of the survey, which is to gather data on coffee prices across different regions to analyze market trends and pricing strategies.
+The introduction reassures participants of the value and importance of their input and provides an estimated completion time of 5 minutes.
+
+Contact information for the survey overseer is clearly listed, with Dr.
+Jane Brewer as the point of contact, providing her email and a contact number to ensure respondents can reach out with questions or require further assistance.
+This transparency builds trust and aids in increasing response rates.
+
+The survey itself comprises a series of well-constructed questions designed to gather comprehensive data while being easy to understand and respond to.
+It starts with basic multiple-choice questions regarding where respondents buy their coffee and how frequently.
+This is followed by checkbox options for the type of coffee they purchase, allowing for multiple selections to capture all preferences.
+The survey progresses to more detailed questions, such as ranking their preferred coffee brands and disclosing their monthly coffee expenditure through an open-ended question.
+Additionally, a simple yes/no question about noticing seasonal price variations is included to gather data on temporal pricing trends.
+
+Each question is strategically ordered from the most straightforward to the more detailed to prevent respondent fatigue and ensure logical flow, maintaining engagement throughout the survey.
+The varied types of questions (multiple-choice, checkboxes, ranking, open-ended, and binary) cater to different data needs and enhance the richness of the data collected, making the analysis more robust.
+
+The survey concludes with a thank-you section, expressing gratitude to the respondents for their time and insights, which reinforces the value of their contribution and ends the survey on a positive note.
+
+For the methodology, a stratified sampling strategy is employed to ensure a diverse and representative sample by dividing the population into subgroups based on geographical regions.
+This approach not only improves the generalizability of the results but also allows for detailed analysis of regional variations in coffee prices.
+Data collection is conducted via an online survey platform, chosen for its wide reach and efficiency, as well as its built-in data validation features to ensure accuracy in the responses gathered.
+
+Data analysis involves quantitative techniques to assess pricing trends and consumer behavior, utilizing statistical software for precision.
+Qualitative responses from open-ended questions undergo thematic analysis to uncover deeper insights.
+This comprehensive analysis approach ensures that both numerical data and rich textual data are effectively utilized.
+
+The overall survey design and methodology are grounded in the literature on survey research, drawing from established frameworks and studies that underscore the effectiveness of such approaches.
+Additionally, preliminary simulations using historical data are conducted to test and refine the survey and sampling strategy, ensuring that the actual data collection is as effective and efficient as possible.
+
+This idealized survey and methodology framework is not only methodically sound and strategically designed but also extensively planned to achieve detailed insights into coffee pricing, thereby fulfilling the objectives set out for this research initiative.
 
@@
 #| label: fig-credibility-interval
-#| fig-cap: "Credibility Interval of Coffee products pricing"
+#| fig-cap: "credibility interval"
 #| eval: true
@@
   Coffee_product_pricing,
-  "areas"
+  "areas",
+  pars = c("old_price", "month", "vendorSaveOnFoods")
 )
-```
-
-```{r}
-#| label: fig-trace-plot
-#| fig-cap: "Trace plot of Coffee products pricing"
-#| eval: true
-#| echo: false
-#| warning: false
-#| message: false
-
-plot(Coffee_product_pricing, "trace")
 ```
@@
 #| fig-subcap: ["Trace plot of Intercept", "Trace plot of old_price", "Trace plot of month", "Trace plot of vendor: SaveOnFoods"]
-#| layout-ncol: 3
+#| layout-ncol: 2
 

### 2024-12-02 models/plumber.R

@@ -1,0 +1,59 @@
+library(plumber)
+library(rstanarm)
+library(tidyverse)
+
+# Load the model
+model <- readRDS("Coffee_product_pricing.rds")
+
+# Define the model version
+version_number <- "0.0.1"
+
+# Define the variables
+variables <- list(
+  old_price = "The previous price of the product, numeric value.",
+  vendor = "The vendor identifier, categorical - Metro or SaveOnFoods",
+  month = "The month of the year, numeric (1 to 12)."
+)
+
+#* @param old_price 
+#* @param vendor 
+#* @param month 
+#* @get /predict_price
+predict_price <- function(old_price = 1.75, vendor = "SaveOnFoods", month = 6) {
+  # Convert inputs to appropriate types
+  old_price <- as.numeric(old_price)
+  vendor <- as.character(vendor)
+  month <- as.integer(month)
+  
+  # Prepare the payload as a data frame
+  payload <- data.frame(
+    old_price = old_price,
+    vendor = vendor,
+    month = month
+  )
+  
+  # Extract posterior samples
+  posterior_samples <- as.matrix(model)  # Convert to matrix for easier manipulation
+  
+  # Define the generative process for prediction
+  beta_old_price <- posterior_samples[, "old_price"]
+  beta_vendor <- posterior_samples[, "vendorSaveOnFoods"]
+  beta_month <- posterior_samples[, "month"]
+  alpha <- posterior_samples[, "(Intercept)"]
+  
+  # Compute the predicted value for the observation
+  predicted_values <- alpha +
+    beta_old_price * payload$old_price +
+    beta_vendor * ifelse(payload$vendor == "SaveOnFoods", 1, 0) +
+    beta_month * payload$month
+  
+  # Predict
+  mean_prediction <- mean(predicted_values)
+  
+  # Store results
+  result <- list(
+    "estimated_price" = mean_prediction
+  )
+  
+  return(result)
+}

### 2024-12-02 scripts/00-simulate_data.R

@@ -21,7 +21,7 @@ Vendors <- c("SaveOnFoods", "Metro")
 
 # Generate simulated data
 simulated_data <- tibble(
-  Vendors = sample(c("Metro", "SaveOnFoods"), size = 1000, replace = TRUE),  # Assumed these are the vendor options
+  Vendors = sample(c("Metro", "SaveOnFoods"), size = 1000, replace = TRUE), # Assumed these are the vendor options
   current_price = round(runif(1000, 0, 500), 3),
   old_price = round(runif(1000, 0, 1000), 3),
   month = sample(1:12, 1000, replace = TRUE),

### 2024-12-02 scripts/01-test_simulated_data.R

@@ -1,12 +1,12 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated vendor's data 
+# Purpose: Tests the structure and validity of the simulated vendor's data
 # Author: Yi Tang
 # Date: today
 # Contact: zachary.tang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
+# Pre-requisites:
+# - The `tidyverse` package must be installed and loaded
+# - 00-simulate_data.R must have been run
 # Any other information needed? None.
 
 

### 2024-12-02 scripts/02-clean_data.R

@@ -20,28 +20,34 @@ product_data <- read_csv("data/01-raw_data/hammer-4-product.csv", show_col_types
 # Combine and clean the data
 combined_data <- raw_data |>
   inner_join(product_data, by = c("product_id" = "id")) |>
-  select(nowtime, 
-         vendor, 
-         product_id, 
-         product_name, 
-         brand, 
-         current_price, 
-         old_price, 
-         units, 
-         price_per_unit)
+  select(
+    nowtime,
+    vendor,
+    product_id,
+    product_name,
+    brand,
+    current_price,
+    old_price,
+    units,
+    price_per_unit
+  )
 
 
 cleaned_data <- combined_data |>
   filter(vendor %in% c("Metro", "SaveOnFoods")) |>
   select(vendor, product_name, current_price, old_price, nowtime) |>
-  mutate(month = month(nowtime),
-         current_price = parse_number(current_price),
-         old_price = parse_number(old_price)) |>
+  mutate(
+    month = month(nowtime),
+    current_price = parse_number(current_price),
+    old_price = parse_number(old_price)
+  ) |>
   filter(str_detect(tolower(product_name), "coffee")) |>
   select(vendor, product_name, current_price, old_price, month) |>
   tidyr::drop_na() |>
   distinct()
 
 #### Save data ####
-write_parquet(x = cleaned_data,
-              sink = "data/02-analysis_data/analysis_data.parquet")
+write_parquet(
+  x = cleaned_data,
+  sink = "data/02-analysis_data/analysis_data.parquet"
+)

### 2024-12-03 paper/paper.qmd
Update paper part
Do some changes about the context and add some reference article into my introduction, fix the rcode problem. Add clean data step in README.

@@
 ---
-title: "Assessing the Multifaceted Influences on Current Coffee Prices"
+title: "Assessing the Various Influences on Current Coffee Prices"
 subtitle: "Coffee Pricing in Canadian Grocery Stores: Current Prices Strongly Shaped by Historical Trends"
@@
 abstract: "This paper investigates the factors influencing coffee product prices in Canadian grocery stores, focusing on historical prices, vendor differences, and seasonal trends.
-Using a Bayesian multiple linear regression model, the study reveals that historical prices have the most significant positive impact on current prices, while vendor differences and seasonal variations also play measurable roles.
+Using a Bayesian multiple linear regression model, the study acknowledge that historical prices have the most significant positive impact on current prices, while vendor differences and seasonal variations also play measurable roles.
 These findings highlight how past prices serve as a benchmark for current pricing strategies, emphasizing the importance of historical data in retail decision-making.
-The results contribute to understanding the dynamics of coffee pricing and provide insights for optimizing retail pricing strategies and future research directions."
+The results contribute to understanding the dynamics of coffee pricing and provide understanding for optimizing retail pricing strategies and future research directions."
 format: pdf
@@
 library(tidyverse)
-library(palmerpenguins)
 library(knitr)
@@
 
-Consuming goods is an integral part of everyone’s daily life, with pricing being a major factor that influences consumer behavior.[@arnot2006ethical] People are particularly interested in the price of goods, and whether there is a price premium or discount.
+Consuming goods is an integral part of everyone’s daily life, with pricing being a major factor that influences consumer behavior.[@huang2014promote] People are particularly interested in the price of goods[@arnot2006ethical], and whether there is a price premium or discount.
 What determines these prices?
@@
 This suggests that vendors heavily rely on historical prices when determining current prices, possibly to maintain a level of consistency that consumers expect.
-Due to a lack of data for some months, it was challenging to establish a definitive analysis of seasonal trends, though this aspect remains an important factor for understanding pricing behavior comprehensively.
+Due to a lack of data for some months, it was challenging to establish a definitive analysis of seasonal trends, though this aspect remains an important factor for understanding pricing behavior completely.
 
@@
 So I only extracted a new variable—month from date of nowtime, which can simplify temporal analysis and identify trends, such as seasonal monthly pattern with price changes or demand patterns.
-It allows grouping data for monthly aggregation and supporting seasonality-focused insights or forecasting models.
+It allows grouping data for monthly aggregation and supporting seasonality-focused understanding or forecasting models.
 
@@
     "The price of the product at the time of observation..",
-    "The specific product being sold, providing product-level insights",
+    "The specific product being sold, providing product-level understanding",
     "The month of data collection, extracted from 'nowtime'"
@@
 To provide an preview of the coffee pricing with all potential factors that might affect it.
-Here, @tbl-sample-analysis-data simply reveals the variation between current price and old price in June for Metro's coffee products.
+Here, @tbl-sample-analysis-data simply explains the variation between current price and old price in June for Metro's coffee products.
 
@@
 
-The dataset from Hammer provides a comprehensive representation of real-world retail activities, capturing key elements such as product details, vendor listings, and price updates.
+The dataset from Hammer provides a wild representation of real-world retail activities, capturing key elements such as product details, vendor listings, and price updates.
 When vendors make updates to product information, including pricing changes or availability adjustments, Hammer gathers and organizes this data into a structured dataset.
@@
 Each record captures a snapshot of a product’s market presence at a given time, enabling targeted analyses like monitoring price fluctuations for specific products, such as coffee.
-By offering such detailed and time-specific information, the dataset provides a valuable foundation for understanding the evolving dynamics of retail pricing and vendor strategies.
+By offering such detailed and time-specific information, the dataset provides a important foundation for understanding the evolving dynamics of retail pricing and vendor strategies.
 
@@
 ```{r}
-#| label: fig-Hist-of-current-price
+#| label: fig-freq-of-current-price
 #| fig-cap: "Frequency of Current Price"
@@
 
-@fig-Hist-of-current-price shows a notable distribution with significant concentrations around 10 and 20 units.
+@fig-freq-of-current-price shows a notable distribution with significant concentrations around 10 and 20 units.
 This suggests a pricing tier system where certain types of coffee products might be grouped by price points due to quality, brand, or other market factors.
@@
 ```{r}
-#| label: fig-Hist-of-old-price
+#| label: fig-freq-of-old-price
 #| fig-cap: "Frequency of Old Price"
@@
 
-According to @fig-Hist-of-old-price, the distribution is mainly focused between 5 and 20 units, pointing to a past market strategy where products were clustered around these prices.
+According to @fig-freq-of-old-price, the distribution is mainly focused between 5 and 20 units, pointing to a past market strategy where products were clustered around these prices.
 The consistency in this price range might reflect a stable market before any recent pricing adjustments influenced by external factors like supplier changes or inflation.
@@
 ```{r}
-#| label: fig-Bar-plot-of-vendor
+#| label: fig-freq-of-vendor
 #| fig-cap: "Frequency of Vendor"
@@
 
-In @fig-Bar-plot-of-old-price, the frequency of products available from Metro significantly surpasses that from SaveOnFoods, suggesting that Metro has a larger share of the market or a wider variety of coffee products.
+In @fig-freq-of-vendor, the frequency of products available from Metro significantly surpasses that from SaveOnFoods, suggesting that Metro has a larger share of the market or a wider variety of coffee products.
 This dominance in product offerings could provide Metro with a competitive edge in attracting a broader customer base.
@@
 ```{r}
-#| label: fig-scatter-plot-of-current-vs-old-price
+#| label: fig-current-vs-old-price
 #| fig-cap: "Current Price vs Old Price"
@@
 
-The positive relationship shown in @fig-scatter-plot-of-current-vs-old-price here indicates that current prices are influenced by their historical prices, maintaining a proportional increase or decrease.
+The positive relationship shown in @fig-current-vs-old-price here indicates that current prices are influenced by their historical prices, maintaining a proportional increase or decrease.
 This trend suggests a pricing policy that adjusts prices based on previous benchmarks while taking into account factors like cost adjustments or market demand.
@@
 ```{r}
-#| label: fig-barplot-of-old-price
+#| label: fig-current-price-by-vendor
 #| fig-cap: "Current Price by Vendor"
@@
 
-@fig-Bar-plot-of-old-price highlights how each vendor prices their products within the market.
+@fig-current-price-by-vendor highlights how each vendor prices their products within the market.
 It shows that both vendors offer a wide range of prices, yet the spread and density of the data points may indicate Metro’s pricing strategy targets both lower and upper market segments, whereas SaveOnFoods might be focusing on a specific niche.
@@
 The outcome variable for this analysis is the current price of coffee products.
-This variable is crucial for understanding the dynamics of pricing in the retail market, as it reflects the final cost faced by consumers.
+This variable is significant for understanding the dynamics of pricing in the retail market, as it reflects the final cost faced by consumers.
 Analyzing the current price helps uncover patterns in how vendors adjust prices over time, respond to market conditions, and compete in a fluctuating retail environment.
@@
 The predictor variables selected from the raw dataset are old price, month, and vendor.
-The old price serves as a predictor because it provides valuable insight into how past pricing decisions influence current prices.
+The old price serves as a predictor because it provides beneficial understanding into how past pricing decisions influence current prices.
 Vendors often make incremental adjustments based on historical pricing data, consumer behavior, and market reactions, which makes it a key factor in understanding pricing strategies.
@@
 
-@fig-trace-plot illustrate that our Bayesian model parameters are converging and demonstrating stability, essential for robust statistical inference.
+@fig-trace-plot-model illustrate that our Bayesian model parameters are converging and demonstrating stability, essential for robust statistical inference.
 The slight oscillation of the intercept around -0.5 indicates minor variability.
@@
 
-In @fig-rhat-plot analysis of coffee product pricing in Canada, the use of the $\hat{R}$ values to assess model convergence reveals that all parameters have $\hat{R}$ values below 1.05, indicating excellent convergence of the model.
+In @fig-rhat-plot analysis of coffee product pricing in Canada, the use of the $\hat{R}$ values to assess model convergence explains that all parameters have $\hat{R}$ values below 1.05, indicating excellent convergence of the model.
 This result validates the reliability of our model in estimating coffee prices and ensures the robustness of the analysis outcomes.
@@
 
-This research conducted a detailed examination of coffee product pricing across major Canadian grocery store chains, specifically Metro and SaveOnFoods.
-By utilizing a regression model, the study uncover how historical price data (by month) can predict current coffee prices.
-This approach not only helped identify pricing trends but also provided a systematic framework to analyze the economic factors influencing those trends.
+This research performed an extensive examination of coffee product pricing across major Canadian grocery store chains, focusing on Metro and SaveOnFoods.
+By employing a regression model, the study analyzed how historical price data (by month) serves as a predictor of current coffee prices.
+This method helped in identifying pricing patterns and provided a structured approach to understand the economic factors influencing those patterns.
+The analysis involved scrutinizing various pricing aspects, ensuring that each factor contributing to the fluctuations was carefully assessed to draw meaningful conclusions.
 
-The findings highlight a dynamic interaction between past and present pricing strategies, underscoring the influence of historical prices on current market behaviors.
-This analysis reveals that historical prices are strong predictors of current prices, suggesting that vendors likely use past data as a benchmark for future pricing decisions.
-This could imply a strategy focused on maintaining market stability and optimizing profit margins, which is crucial in a competitive retail environment.
+The findings highlight a dynamic relationship between past and present pricing strategies, emphasizing the role of historical prices in shaping current market behaviors.
+The analysis indicates that historical prices strongly influence current prices, suggesting that vendors often rely on previous data when determining future pricing decisions.
+This approach appears to be aimed at ensuring stability in the market and optimizing profit margins, which is important in a highly competitive retail environment.
+By maintaining consistency in pricing and leveraging historical trends, vendors might be focusing on strategies to attract and retain customers, avoid sudden price changes, and manage costs effectively.
+The reliance on historical pricing data allows vendors to make informed decisions that minimize risks associated with unexpected market changes.
+Additionally, it suggests that these pricing strategies are designed to foster consumer trust by providing predictable price points, which is particularly important in sustaining customer loyalty and enhancing brand perception in a highly volatile market.
+
+Moreover, the study also provides observation into how price stability can help in inventory management and supply chain optimization.
+By using historical data as a benchmark, vendors can better predict demand patterns, allowing them to streamline their logistics and reduce overhead costs.
+This, in turn, helps maintain a balance between supply and demand, ultimately leading to enhanced operational efficiency.
+In a market where even small fluctuations can have a significant impact on consumer purchasing decisions, understanding the relationship between historical and current prices is quite necessary for developing effective pricing strategies that ensure both profitability and competitiveness.
 
@@
 
-The coffee products prices are influenced by more than just historical trends; they also respond to a range of external economic factors.
-The study highlights how variations in coffee prices align with broader economic indicators like inflation rates and consumer demand.
-This insight is crucial for understanding the dynamic nature of the coffee market, suggesting that vendors adjust their pricing strategies not only based on past price behavior but also in reaction to economic conditions.
-This deeper understanding of price adjustments helps illustrate the broader economic landscape within which these businesses operate, emphasizing the strategic decisions vendors make in response to economic pressures.
-This analysis significantly enriches our understanding of market behaviors and the economic strategies that drive vendor actions in the competitive grocery sector.
+The coffee product prices are influenced by more than just historical trends; they also react to various external economic factors.
+This study shows how changes in coffee prices align with broader economic indicators, such as inflation rates and shifts in consumer demand.
+These patterns are essential for understanding the complexities of the coffee market, implying that vendors adjust their pricing strategies in response to both past price trends and the changing economic landscape.
+The analysis illustrates how vendors take into account inflation, fluctuations in demand, and other economic conditions when determining prices.
+These considerations help us understand the broader market environment in which these businesses operate, highlighting the strategic choices vendors make to navigate economic pressures, maintain competitiveness, and adapt to consumer expectations.
+
+Furthermore, the influence of external factors, such as changes in import tariffs, fluctuations in exchange rates, and variations in production costs, also plays a significant role in determining coffee prices.
+Vendors must continuously monitor these factors to adjust their pricing strategies accordingly.
+For instance, an increase in production costs due to higher raw material prices may necessitate a corresponding increase in retail prices to maintain profit margins.
+Similarly, changes in consumer behavior, such as a shift towards premium coffee products or an increased preference for organic options, can also impact pricing strategies.
+Vendors need to adapt to these trends to remain relevant in the market and meet evolving consumer expectations.
+
+The study also points out how macroeconomic indicators, like interest rates and employment levels, indirectly affect coffee pricing.
+Higher interest rates may lead to reduced consumer spending power, prompting vendors to adjust their pricing strategies to maintain sales volume.
+On the other hand, lower unemployment rates could lead to increased disposable income, allowing vendors to explore opportunities for premium pricing.
+These dynamic interactions between external economic factors and pricing decisions underscore the need for a flexible and responsive pricing strategy that can adapt to changes in the broader economic environment.
+By understanding these relationships, vendors can develop more resilient pricing models that not only respond to immediate market conditions but also anticipate future economic shifts.
 
@@
 ### Limitation
-This study integrates two distinct raw datasets to construct the analysis dataset, which presents unique challenges due to varying variable names and formats.
-The process involved carefully aligning these variables to ensure consistency and accuracy in the dataset used for modeling.
-This integration underscores the importance of meticulous data preparation in ensuring the reliability of the results obtained from statistical analyses.
 
-A significant limitation of this study is the absence of geographic data for the vendors.
-Although our analysis provides insights into the pricing strategies of Metro and SaveOnFoods, we lack the data to explore how geographical location influences pricing strategies across Canada.
-Metro and SaveOnFoods operate in different regions of Canada, potentially the Eastern and Western parts, and it is plausible that regional economic conditions, competition, and consumer demographics could affect pricing strategies.
-The absence of this data restricts our ability to analyze and understand regional pricing dynamics comprehensively.
-lack of month: only have data of coffee prouduct pricing in June to November.
+This study involved integrating two separate raw datasets to build the analytical dataset, which presented challenges due to differing variable names and formats.
+The integration process required aligning these variables accurately to ensure consistency in the final dataset used for modeling.
+This emphasizes the importance of proper data preparation to ensure reliable results from statistical analyses.
+The process of integrating data from different sources is inherently complex and requires careful attention to detail to avoid errors that could compromise the validity of the findings.
+Ensuring that the data is clean, consistent, and accurately aligned is fundamental to producing meaningful and trustworthy results.
+
+A major limitation of this study is the absence of geographic information for the vendors.
+While the analysis provides useful observations on the pricing strategies of Metro and SaveOnFoods, it does not include information that could show how pricing varies by geographical region across Canada.
+Metro and SaveOnFoods operate in different parts of the country, potentially representing Eastern and Western Canada.
+It is possible that differences in regional economic conditions, levels of competition, and consumer demographics affect pricing strategies.
+The lack of geographic data prevents a deeper analysis of regional pricing variations and limits the ability to fully understand how local factors influence pricing decisions.
+Moreover, this study only covers coffee product pricing data from June to November, meaning that we miss the impact of full-year seasonality on pricing.
+
+In addition to the absence of geographic data, another limitation is the lack of information regarding promotional activities and discounts.
+Promotions play a significant role in influencing consumer purchasing decisions, and without this data, it is challenging to fully understand the factors driving price changes.
+Promotional campaigns, such as discounts or bundle provides, can have a considerable impact on sales volume and pricing strategies, and their absence from the dataset limits the scope of the analysis.
+Including this data in future research would provide a more broad view of the factors influencing pricing decisions and help to better understand the interplay between promotional activities and price adjustments.
 
 ### Weaknesses and next steps
-While the model provides valuable insights, there are limitations due to the dataset only covering a short period (June to November).
-This limits the ability to analyze long-term trends or seasonal impacts beyond this timeframe.
-Additionally, the model assumes linear relationships among variables, which may not fully capture more complex dynamics in price fluctuations.
 
-Future research could expand the timeframe of data collection to include multiple years to better understand long-term trends and seasonal variations.
-Incorporating additional variables such as promotional activities, competitor prices, and economic indicators could also enrich the analysis.
-Further, exploring non-linear models or machine learning approaches may provide deeper insights into the pricing strategies of different vendors.
-To address these limitations, future research should focus on acquiring and integrating geographic data into the analysis.
-This would allow for a more detailed examination of how location-specific factors influence pricing, enhancing our understanding of regional market behaviors.
-Exploring geographical influences on pricing can reveal targeted strategies that vendors might use to cater to local consumer preferences or to respond to regional competition.
-Incorporating such data would significantly enrich the analytical framework and potentially yield insights that could inform more localized or region-specific business strategies for these vendors.
+The model provides useful observations; however, there are certain limitations due to the dataset's short time frame, spanning only from June to November.
+This short time frame restricts our ability to analyze long-term trends or seasonal impacts beyond this period.
+Additionally, the model assumes linear relationships between the variables, which may not fully represent the complexity of price fluctuations driven by diverse factors, including consumer behavior and market conditions.
+The linearity assumption may oversimplify the relationships between variables, potentially overlooking non-linear dynamics that could provide a deeper understanding of the factors influencing pricing.
+
+Future research should extend the data collection period to cover multiple years, which would allow for a more thorough understanding of long-term trends and seasonal price variations.
+Including additional variables, such as promotional activities, competitor pricing, and broader economic indicators, could further enrich the analysis.
+Exploring more complex models, such as non-linear methods or machine learning techniques, may also reveal deeper connections within the data and offer a more detailed understanding of the pricing strategies used by different vendors.
+Future studies should also prioritize obtaining geographic data to allow a detailed study of location-specific influences on pricing.
+This would enable a more subtle analysis of how regional factors, such as differences in consumer preferences and local market competition, impact pricing strategies.
+By incorporating geographic data, future research could provide observation into more localized or region-specific strategies that vendors use, helping to better understand how they adapt to regional differences and tailor their strategies accordingly.
+
+Expanding the scope of the research to include qualitative data, such as consumer feedback and vendor interviews, could also provide a richer context for understanding pricing strategies.
+Qualitative observation could help uncover the motivations behind pricing decisions, offering a perspective that quantitative data alone cannot provide.
+Additionally, incorporating machine learning algorithms could enhance the predictive accuracy of the model by capturing non-linear relationships and complex interactions between variables.
+Machine learning approaches, such as decision trees or neural networks, could offer a more sophisticated analysis of pricing dynamics and help identify hidden patterns that are not immediately apparent through traditional regression models.
+
+Future research could also explore the impact of external shocks, such as supply chain disruptions or sudden changes in consumer preferences, on pricing strategies.
+By analyzing how vendors respond to unexpected events, researchers could gain a better understanding of the resilience and adaptability of pricing models in the face of uncertainty.
+This would provide helpful understanding into the strategies that vendors use to mitigate risks and maintain stability in times of economic turbulence.
+Furthermore, examining the role of consumer loyalty programs and their effect on pricing strategies could add another layer of depth to the analysis, as these programs often influence purchasing behavior and price sensitivity.
+
+By addressing these limitations and expanding the scope of the research, future studies could provide a more overall understanding of the factors that influence coffee pricing in the Canadian retail market.
+This would not only enhance our understanding of vendor strategies but also provide beneficial information for policymakers, industry stakeholders, and consumers looking to navigate the complexities of the coffee market.
 
@@
 
-To address the collection of data regarding coffee prices through an idealized survey and methodology, we have meticulously designed a survey that aligns with best practices in research and data collection[@citedata].
-The survey begins with an introductory section, welcoming participants to the "Coffee Price Insights Survey." This introduction serves to inform respondents of the purpose of the survey, which is to gather data on coffee prices across different regions to analyze market trends and pricing strategies.
+To address the collection of data regarding coffee prices through an idealized survey and methodology, we have accurately designed a survey that aligns with best practices in research and data collection[@citedata].
+The survey begins with an introductory section, welcoming participants to the "Coffee Price perspective Survey." This introduction serves to inform respondents of the purpose of the survey, which is to gather data on coffee prices across different regions to analyze market trends and pricing strategies.
 The introduction reassures participants of the value and importance of their input and provides an estimated completion time of 5 minutes.
@@
 
-The survey itself comprises a series of well-constructed questions designed to gather comprehensive data while being easy to understand and respond to.
+The survey itself comprises a series of well-constructed questions designed to gather all datas while being easy to understand and respond to.
 It starts with basic multiple-choice questions regarding where respondents buy their coffee and how frequently.
@@
 
-The survey concludes with a thank-you section, expressing gratitude to the respondents for their time and insights, which reinforces the value of their contribution and ends the survey on a positive note.
+The survey concludes with a thank-you section, expressing gratitude to the respondents for their time and understanding, which reinforces the value of their contribution and ends the survey on a positive note.
 
@@
 Data analysis involves quantitative techniques to assess pricing trends and consumer behavior, utilizing statistical software for precision.
-Qualitative responses from open-ended questions undergo thematic analysis to uncover deeper insights.
-This comprehensive analysis approach ensures that both numerical data and rich textual data are effectively utilized.
+Qualitative responses from open-ended questions undergo thematic analysis to uncover deeper understanding.
+This analysis approach ensures that both numerical data and rich textual data are effectively utilized.
 
@@
 
-This idealized survey and methodology framework is not only methodically sound and strategically designed but also extensively planned to achieve detailed insights into coffee pricing, thereby fulfilling the objectives set out for this research initiative.
+This idealized survey and methodology framework is not only methodically sound and strategically designed but also extensively planned to achieve detailed understanding into coffee pricing, thereby fulfilling the objectives set out for this research initiative.
 
@@
 ```{r}
-
 #| echo: false
-#| eval: true
 #| message: false
 #| warning: false
-#| label: fig-trace-plot
-#| fig-cap: "Trace plot of Party"
-#| fig-subcap: ["Trace plot of Intercept", "Trace plot of old_price", "Trace plot of month", "Trace plot of vendor: SaveOnFoods"]
+#| label: fig-trace-plot-model
+#| fig-cap: "Trace plot of variables"
+#| fig-subcap: ["Trace plot of Intercept", "Trace plot of old price", "Trace plot of month", "Trace plot of vendor: SaveOnFoods"]
 #| layout-ncol: 2

### 2024-12-04 paper/paper.qmd
Update all part
Do the final fixation of all of my parts, such as the name of fig-cap, readme.

@@
 
+library(caret)
 library(tidyverse)
@@
 This paper seeks to answer some of these questions by combining product data from Canadian grocery stores with additional raw data to identify key factors that influence product pricing.
-Specifically, we focus on coffee products and use the current price as the outcome variable, aiming to understand the influences behind it.
+Specifically, we focus on coffee products and use the current price as the outcome variable, trying to understand the influences behind it.
 
 To explore this, I chose one of the most intuitive factors: the old price, since historical pricing often influences how vendors set current prices.
+The relationship between previous and current pricing can provide observation into whether vendors maintain consistency or adjust prices in response to market conditions.
 Additionally, I included data from two vendors—Metro and SaveOnFoods—located in different parts of Canada to investigate any differences in pricing strategies between the eastern and western regions.
-The inclusion of month allows us to explore potential seasonal trends in coffee pricing, assessing whether specific times of the year see significant price variations.
+This distinction between vendors allows us to better understand regional variations and how local competition might impact pricing.
+The inclusion of the month variable allows us to explore potential seasonal trends in coffee pricing, assessing whether specific times of the year see significant price variations, possibly due to fluctuations in demand or promotional campaigns.
+By evaluating these factors, we can determine the extent to which historical pricing, regional differences, and seasonality drive current pricing decisions in the coffee market.
 
@@
 Using a Bayesian multiple linear regression model, I estimated these effects to better understand the pricing dynamics of coffee products and to determine how much each factor contributes to pricing decisions in the market.
+This modeling approach provides a probabilistic framework that accounts for uncertainty in the estimates, allowing for more nuanced conclusions compared to traditional methods.
 
@@
 This suggests that vendors heavily rely on historical prices when determining current prices, possibly to maintain a level of consistency that consumers expect.
-Due to a lack of data for some months, it was challenging to establish a definitive analysis of seasonal trends, though this aspect remains an important factor for understanding pricing behavior completely.
+Consistency in pricing is often valued by consumers, as it fosters a sense of trust and predictability.
+Due to a lack of data for some months, it was challenging to establish a definitive analysis of seasonal trends, though this aspect remains an important factor for understanding pricing behavior comprehensively.
+Seasonal patterns can have substantial effects on consumer behavior, and thus their absence in the dataset may limit the scope of understanding regarding periodic fluctuations in coffee prices.
 
-The paper is structured as following: @sec-data describes the data used for analysis, @sec-model describes how to set up, justify and validate the model, @sec-result tells the finding of the data and model, @sec-discussion discusses the implication, potential problems, and future expectations.
+The paper is structured as follows: @sec-data describes the data used for analysis, providing details on data collection methods and any preprocessing required.
+@sec-model discusses how to set up, justify, and validate the Bayesian multiple linear regression model, explaining the rationale for selecting this approach and detailing the assumptions made.
+@sec-result presents the findings derived from the data and model, highlighting the main effects and relationships observed.
+Finally, @sec-discussion delves into the implications of the results, addresses potential limitations, and outlines expectations for future research, considering how expanding the dataset or incorporating additional variables might enhance our understanding of coffee pricing dynamics.
 
@@
 
-## Overview
+## Data Source
 
@@
 
+## Inspiration on data organization
+
 In order to simulate data, test simulated data, clean data, test cleaned data, exploratory data analysis and model data, we used R programming language [@citeR] to analyze the data and plot the graphs.
@@
 I also referenced many of the examples and techniques provided by Telling Stories with Data [@alexander2023telling], which helped me understand how to visualize the data and communicate the findings effectively.
-Specific libraries that assisted the analysis include `tidyverse` [@citetidyverse], `knitr` [@citeknitr], `arrow` [@citearrow], `ggplot2` [@citeggplot2],  `dplyr` [@citedplyr],  `here` [@citehere], `kableExtra` [@citekableExtra], `gridExtra`[@citegridExtra], `modelsummary`[@citemodelsummary], `rstanarm`[@citerstanarm].
+Specific libraries that assisted the analysis include `tidyverse` [@citetidyverse],`caret`[@citecaret], `janitor`[@citejanitor], `lubridate`[@citelubridate],  `knitr` [@citeknitr], `arrow` [@citearrow], `ggplot2` [@citeggplot2],  `dplyr` [@citedplyr],  `here` [@citehere], `kableExtra` [@citekableExtra], `gridExtra`[@citegridExtra], `styler`[@citestyler], `plumber`[@citeplumber] `modelsummary`[@citemodelsummary], `rstanarm`[@citerstanarm].
 
 The inspiration for my data processing came from my desire to study what factors would affect the current price of coffee products from two vendors in different regions of Canada, such as the current price of coffee products from two vendors, Metro and SaveOnFoods.
-@tbl-variable are the data I selected after cleaning the data, and new variable `month` extracted and transformed from raw data also.
+@tbl-variable are the data I selected after cleaning the data, and new variable month extracted and transformed from raw data also.
 
@@
 #| label: tbl-variable
-#| tbl-cap: "Variables and their Definitions for the Coffee Product Pricing."
+#| tbl-cap: "Variables for the Coffee Product Pricing."
 #| echo: false
@@
   Definition = c(
-    "The retailer selling the product in Canada.",
-    "The historical price of the product, showing previous pricing or discounts.",
-    "The price of the product at the time of observation..",
+    "The retailer selling the product in Canada",
+    "The historical price of the product, showing previous pricing or discounts",
+    "The price of the product at the time of observation",
     "The specific product being sold, providing product-level understanding",
@@
 
-kable(variable_table, col.names = c("Variable", "Definition"),
-      format = "latex", booktabs = TRUE, linesep = "") %>%
+kable(variable_table,
+  col.names = c("Variable", "Definition"),
+  format = "latex", booktabs = TRUE, linesep = ""
+) %>%
   column_spec(1, bold = TRUE, width = "15em") %>%
@@
 #| label: fig-freq-of-current-price
-#| fig-cap: "Frequency of Current Price"
+#| fig-cap: "Right-skewed distribution of Current Price"
 #| message: false
@@
 #| label: fig-freq-of-old-price
-#| fig-cap: "Frequency of Old Price"
+#| fig-cap: "Right-skewed of Old Price"
 #| message: false
@@
   theme_minimal()
-
 ```
@@
 #| label: fig-freq-of-vendor
-#| fig-cap: "Frequency of Vendor"
+#| fig-cap: "Higher frequency on Metro compared to SaveOnFoods"
 #| message: false
@@
 #| label: fig-current-vs-old-price
-#| fig-cap: "Current Price vs Old Price"
+#| fig-cap: "Strong positive correlation between old and current prices for both vendors"
 #| message: false
@@
 #| label: fig-current-price-by-vendor
-#| fig-cap: "Current Price by Vendor"
+#| fig-cap: "Similar median prices for both vendor and a wider range plus more outliers in Metro"
 #| message: false
@@
 
-The Bayesian Multiple Linear Regression (MLR) model is a suitable choice for analyzing the relationship between `current price` (the dependent variable) and the predictors in the dataset.
+We considered an alternative model, the frequentist model, but ultimately did not select it.
+We conducted a training and testing dataset split and compared their prediction power, particularly looking at the Mean Squared Error (MSE).
+The results showed that the Bayesian Multiple Linear Regression (MLR) had a lower MSE, making it a better fit for our data.
+Additionally, the Bayesian approach provides greater flexibility.
+
+The Bayesian Multiple Linear Regression (MLR) model is a suitable choice for analyzing the relationship between the current price (the dependent variable) and the predictors in the dataset.
 The dependent variable is continuous, and the Bayesian framework assumes a normal distribution for the response, which aligns well with the nature of coffee prices.
-This model captures the linear relationships between `old price` (continuous), `vendor` (categorical, represented as a dummy variable), and `month` (numeric).
-These predictors are assumed to have additive effects on the response, which fits the linear regression framework.
-Logistic regression is used when the outcome variable is binary (e.g.
-0 or 1).
-However, in our dataset, the dependent variable, `current price`, is continuous.
+This model captures the linear relationships between the old price (continuous), vendor (categorical, represented as a dummy variable), and month (numeric).
+These predictors are assumed to have additive effects on the response, fitting the linear regression framework.
+
+Logistic regression is used when the outcome variable is binary (e.g., 0 or 1).
+However, in our dataset, the dependent variable, current price, is continuous.
 Since logistic regression cannot model continuous outcomes, it is unsuitable for this analysis.
-Also, poisson or negative binomial regression is typically applied when the response variable represents count data (e.g., the number of events occurring in a fixed period).
-`current_price` does not represent counts but rather continuous pricing data.
-Thus, these models do not align with the nature of the dependent variable.
+Similarly, Poisson or negative binomial regression is typically applied when the response variable represents count data (e.g., the number of events occurring in a fixed period).
+Since the current price represents continuous pricing data rather than counts, these models do not align with the nature of the dependent variable.
+
+The final results indicate that the Bayesian MLR model outperforms the frequentist model in terms of both flexibility and predictive performance, which led us to choose the Bayesian MLR model for our analysis.
 
@@
 
-@tbl-model-summary indicates a strong fit with a high $R^2$ of 0.900, suggesting a strong explanatory power of the model regarding the variance in coffee product prices.
-The model's parameters show that the old price of coffee (coefficient = 0.77) has a significant positive influence on the current price, suggesting that past pricing trends are good predictors of current pricing strategies.
-Vendor impact, specifically SaveOnFoods, shows a negative association with current price (coefficient = -0.61), indicating that coffee products from SaveOnFoods tend to be cheaper compared to Metro.
-Additionally, the month coefficient (0.06) implies a slight monthly variation in coffee pricing.
-The model's predictive performance is validated by low WAIC and LOOIC scores, and a small RMSE of 1.75, enhancing confidence in the reliability of its predictions.
+The analysis of coffee pricing in Canadian grocery stores several key observations based on the Bayesian multiple linear regression model.
+The model effectively captures the dynamics of pricing strategies employed by vendors and highlights the influence of historical price, vendor differences, and seasonal trends on current prices.
+@tbl-model-summary indicates a strong fit with a high $R^2$ of 0.900, indicating that approximately 90% of the variance in coffee prices is explained by the included predictors.
+This strong fit suggests the chosen factors—historical prices, vendor characteristics, and month—are significant in determining current coffee pricing.
+The coefficient for the historical price variable was found to be 0.77, indicating a strong positive effect on the current price.
+This means that higher past prices tend to lead to higher current prices, suggesting that vendors are consistent in maintaining pricing trends over time.
+The strong relationship between historical and current prices suggests that coffee vendors may to ensure price stability, which could be beneficial for maintaining customer loyalty and trust, as consumers often prefer predictable and steady pricing.
 
-@fig-credibility-interval llustrates the posterior distributions for the parameters in your Bayesian regression model, analyzing factors influencing coffee prices.
-The intercept shows a slight positive baseline effect.
-The old price of coffee strongly and positively affects the current price, indicating a direct relationship.
-The month variable shows a minimal and variable impact.
-SaveOnFoods, as a vendor, is associated with lower prices compared to Metro.
-The sigma parameter, indicating the model's error variance, shows a sharp and precise estimation, suggesting consistent variability in the data explained by the model.
+The model shows a significant difference between the two vendors, Metro and SaveOnFoods.
+Specifically, SaveOnFoods has a negative association with current price levels, with a coefficient of -0.61.
+This indicates that SaveOnFoods tends to offer coffee products at lower prices compared to Metro, which may point to different pricing strategies or market positioning.
+SaveOnFoods may focus on affordability and competitive pricing to attract cost-sensitive consumers, whereas Metro might position its products as more premium, thereby maintaining higher price points.
+The coefficient for the month variable, 0.06, suggests that there is a slight but consistent increase in prices over time, reflecting potential seasonal variations in demand or pricing adjustments throughout the year.
+This indicates that factors like holidays, consumer buying habits, and promotional events could have an impact on pricing patterns, although, due to the short data collection period, definitive conclusions regarding seasonal trends are limited.
+Expanding the data collection period to include more months or years would provide a clearer understanding of these seasonal trends and their impact on pricing.
+
+@fig-credibility-interval illustrates the posterior distributions for the parameters were consistent with the priors, providing stability in the estimates.
+This consistency indicates that the model's assumptions and data align well, reinforcing the reliability of the estimated effects.
+Notably, the vendor parameter for SaveOnFoods diverged more significantly, which might indicate unique pricing behaviors that warrant further investigation.
+SaveOnFoods may be employing specific pricing tactics that differ considerably from Metro, such as frequent promotional discounts or region-specific pricing strategies.
+Understanding these unique behaviors could help to explain why SaveOnFoods consistently offers lower prices.
+The model's reliability is further validated by a low RMSE of 1.75 and satisfactory WAIC and LOOIC scores, which collectively support the model's accuracy in predicting current prices.
+The greatness of these metrics suggests that the model can effectively be used to understand pricing strategies in the broader retail context.
+
+The distribution of current prices shows significant concentration around specific price points, potentially due to product quality or brand categorization.
+For instance, certain brands or types of coffee might be priced consistently across different vendors, creating clusters of similar price points.
+Similarly, historical prices display consistency, suggesting stable pricing strategies among vendors, which could be influenced by factors like cost of production, supply chain considerations, and consumer preferences.
+The frequency analysis highlights Metro's larger product offering compared to SaveOnFoods, which may provide Metro with a competitive edge in variety and customer attraction.
+A greater variety of products allows Metro to cater to a wider range of consumer preferences, potentially attracting both premium and budget-conscious customers.
+This variety might enable Metro to occupy different segments of the market, thereby enhancing its overall market presence.
+
+The results suggest that vendors rely heavily on historical prices to set current prices, maintaining a level of consistency that is likely focused on fostering consumer trust.
+Consumers often associate consistent pricing with reliability, which can help build brand loyalty and repeat purchasing behavior.
+The pricing differences between Metro and SaveOnFoods may also reflect distinct regional market strategies or consumer demographics.
+For example, SaveOnFoods might operate in regions with a higher sensitivity to pricing, leading it to adopt more competitive price levels.
+Metro, on the other hand, may cater to areas where consumers are willing to pay a premium for perceived quality or brand reputation.
+Seasonal factors, although not extensively captured due to data limitations, do show some influence on pricing adjustments over time.
+Seasonal trends such as increased demand during the holiday season or promotional events might cause temporary price hikes, which could be better understood with a more extended dataset.
+Incorporating data from a full year or multiple years could provide more substantial evidence of these seasonal effects, enhancing the understanding of how temporal factors shape pricing strategies.
+
+Overall, this analysis underscores the importance of historical pricing, vendor differences, and seasonal influences in determining coffee prices in Canadian grocery stores.
+The reliance on historical data helps vendors ensure price stability, which can be a key factor in maintaining customer satisfaction.
+Vendor-specific strategies, such as those seen with SaveOnFoods' lower pricing, indicate that different retailers may adopt distinct approaches to appeal to their target markets.
+Understanding these dynamics can help vendors refine their pricing strategies, optimize inventory management, and ultimately enhance their market competitiveness.
+Future research could benefit from a longer data collection period and the inclusion of additional variables such as promotional activities, consumer demographics, and regional economic conditions to provide a more  view of coffee pricing dynamics.
 
@@
 The analysis indicates that historical prices strongly influence current prices, suggesting that vendors often rely on previous data when determining future pricing decisions.
-This approach appears to be aimed at ensuring stability in the market and optimizing profit margins, which is important in a highly competitive retail environment.
+This approach appears to be focused at ensuring stability in the market and optimizing profit margins, which is important in a highly competitive retail environment.
 By maintaining consistency in pricing and leveraging historical trends, vendors might be focusing on strategies to attract and retain customers, avoid sudden price changes, and manage costs effectively.
@@
 #| fig-cap: "PPcheck & Posterior vs Prior"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+#| fig-subcap: ["Model predictions ($y_{rep}$) closely align with observed data ($y$)", "Posterior estimates are more precise compared to prior especially for vendrSaveOnFoods and (Intercept)"]
 
@@
 #| label: tbl-model-summary
-#| tbl-cap: "Model summary of Coffee product pricing"
+#| tbl-cap: "Good prediction accuracy with $R^2$ of 0.900 and RMSE of 1.75"
 #| eval: true
@@
 )
+```
 
-```
+\newpage
 
@@
 #| label: fig-credibility-interval
-#| fig-cap: "credibility interval"
+#| fig-cap: "Credible intervals indicate high certainty for old price and lower certainty for other parameters"
 #| eval: true
@@
 plot(Coffee_product_pricing, "trace", "vendorSaveOnFoods")
-
 ```
@@
 #| label: fig-rhat-plot
-#| fig-cap: "R-hat plot of Coffee products pricing"
+#| fig-cap: "Good convergence with Rhat values close to 1"
 #| eval: true
@@
 
-\newpage
+\clearpage
 

### 2024-12-04 scripts/02-clean_data.R

@@ -45,7 +45,7 @@ cleaned_data <- combined_data |>
   select(vendor, product_name, current_price, old_price, month) |>
   tidyr::drop_na() |>
   distinct()
-
+write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")
 #### Save data ####
 write_parquet(
   x = cleaned_data,

### 2024-12-04 scripts/05-model_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Development and validation of a Bayesian regression model for predicting coffee product pricing based on historical data
+# Purpose: Development and validation of two different model for predicting coffee product pricing based on historical data
 # Author: Yi Tang
 # Date: today
 # Contact: zachary.tang@mail.utoronto.ca
@@ -14,6 +14,7 @@
 library(tidyverse)
 library(rstanarm)
 library(arrow)
+library(caret)
 
 #### Read data ####
 analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
@@ -30,8 +31,66 @@ Coffee_product_pricing <-
     seed = 304
   )
 
-#### Save model ####
+#### Save Bayesian model ####
 saveRDS(
   Coffee_product_pricing,
   file = "models/Coffee_product_pricing.rds"
 )
+
+# Frenquentist model
+
+Coffee_product_pricing2 <- glm(current_price ~ old_price + month + vendor,
+  data = analysis_data,
+  family = gaussian()
+)
+
+#### Save Frenquentist model ####
+saveRDS(
+  Coffee_product_pricing2,
+  file = "models/Coffee_product_pricing2.rds"
+)
+
+# Train-Test Split
+
+set.seed(304)
+train_indices <- sample(1:nrow(analysis_data), size = 0.8 * nrow(analysis_data))
+train_data <- analysis_data[train_indices, ]
+test_data <- analysis_data[-train_indices, ]
+
+# Fit the stan_glm model
+
+# Set the final coffee product pricing model
+Coffee_product_pricing <-
+  stan_glm(
+    formula = current_price ~ old_price + month + vendor,
+    data = analysis_data,
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_aux = exponential(rate = 1, autoscale = TRUE),
+    seed = 304
+  )
+
+# Fit the glm model
+Coffee_product_pricing2 <- glm(
+  formula = current_price ~ month + vendor + old_price,
+  data = train_data,
+  family = gaussian()
+)
+
+# Predictions on the test set
+# For stan_glm
+stan_preds <- posterior_predict(Coffee_product_pricing, newdata = test_data)
[…]

### 2024-12-15 paper/paper.qmd
Update context of paper
Delete useless word or snetences and add useful information.

@@
 Using a Bayesian multiple linear regression model, I estimated these effects to better understand the pricing dynamics of coffee products and to determine how much each factor contributes to pricing decisions in the market.
-This modeling approach provides a probabilistic framework that accounts for uncertainty in the estimates, allowing for more nuanced conclusions compared to traditional methods.
+This modeling approach provides a probabilistic framework that accounts for uncertainty in the estimates.
+And it allows for more detailed conclusions compared to normal methods.
 
@@
 Due to a lack of data for some months, it was challenging to establish a definitive analysis of seasonal trends, though this aspect remains an important factor for understanding pricing behavior comprehensively.
-Seasonal patterns can have substantial effects on consumer behavior, and thus their absence in the dataset may limit the scope of understanding regarding periodic fluctuations in coffee prices.
+Time variable can have substantial effects on consumer behavior, and thus their absence in the dataset may limit the scope of understanding regarding periodic fluctuations in coffee prices.
 
@@
 Since the variable nowtime only records 4 months, it is considered a lack of Long-Term Trends, which means it's difficult to identify long-term pricing or demand patterns by using short data periods.
-So I only extracted a new variable—month from date of nowtime, which can simplify temporal analysis and identify trends, such as seasonal monthly pattern with price changes or demand patterns.
-It allows grouping data for monthly aggregation and supporting seasonality-focused understanding or forecasting models.
+So I only extracted a new variable—month from date of nowtime, which can figure out the problem of lacking data of time variable.
 
@@
 
-The dataset from Hammer provides a wild representation of real-world retail activities, capturing key elements such as product details, vendor listings, and price updates.
+The dataset from Hammer provides a representation of real-world retail activities, includingg key elements such as product details, vendor listings, and price updates currently and historically.
 When vendors make updates to product information, including pricing changes or availability adjustments, Hammer gathers and organizes this data into a structured dataset.
-This ensures that the dataset remains accurate and reflective of current retail conditions.
+This ensures that the dataset remains accurance and reflective of current retail conditions.
 
-The dataset includes essential fields such as vendor, product name, current price, old price, and a timestamp referred to as nowtime.
-The data is collected through scraping and is systematically structured to support an in-depth analysis of retail trends, pricing strategies, and overall market dynamics across different periods.
-Each record captures a snapshot of a product’s market presence at a given time, enabling targeted analyses like monitoring price fluctuations for specific products, such as coffee.
-By offering such detailed and time-specific information, the dataset provides a important foundation for understanding the evolving dynamics of retail pricing and vendor strategies.
+The dataset includes vendor, product name, current price, old price, and a times variable referred to nowtime.
+The data is collected through scraping and is systematically structured to support an in-depth analysis of retail trends, potential pricing relationships, and overall market dynamics across different periods.
+Each record captures a snapshot of a product’s market presence at a given time, enabling targeted analyses like monitoring fluctuation between current and historical price for specific products, such as coffee which is the product type the paper wants to analyze.
+By offering such detailed and time-specific information, the dataset provides a important foundation for understanding the evolving dynamics of retail pricing and potential impact.
 
@@
 The predictor variables selected from the raw dataset are old price, month, and vendor.
-The old price serves as a predictor because it provides beneficial understanding into how past pricing decisions influence current prices.
-Vendors often make incremental adjustments based on historical pricing data, consumer behavior, and market reactions, which makes it a key factor in understanding pricing strategies.
+The old price serves as a predictor because it provides how past pricing decisions influence current prices.
+Vendors often make incremental adjustments based on historical pricing data, consumer behavior, and market reactions, which makes it a key factor in understanding why price changing in some way.
 Month is included to account for possible seasonal trends in pricing, as consumer demand and promotional activities often vary throughout the year, potentially impacting coffee prices.
